Effect of Election on Currency Fluctuation

### 2024-04-12 paper/paper.qmd
created a datasheet text file and pasted in a template, will change content in future. Also revised structure of the paper

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

@@

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

@@

analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it.

>>>>

## Data on Exchange Rate

@@

## Data on Election Results

### Selection of Data Source

@@

### Construction of Inauguration Week
